Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-12-23 journal paper/content/sec-bg.tex
Removed some \newpage, minor edit.

We present self-contained background on multi-armed bandits (MAB), to make the paper accessible to researchers who are not experts on MAB. More details can be found in any of the monographs
\citep{Bubeck-survey12,slivkins-MABbook,LS19bandit-book}.

@@

Some MAB algorithms, \eg Thompson Sampling, are Bayesian: they input a prior on mean rewards, and attain strong Bayesian guarantees (in expectation over the prior) when the prior is correct. Such algorithms can also be initialized with some simple `fake' priors; in fact, this is how Thompson Sampling can be made to satisfy the optimal regret bounds listed above.

>>>>

We present self-contained background on multi-armed bandits (MAB), to make the paper accessible to researchers who are not experts on MAB. More details can be found in books 
\citep{Bubeck-survey12,slivkins-MABbook,LS19bandit-book}.

@@

Some MAB algorithms, \eg Thompson Sampling, are Bayesian: they input a prior on mean rewards, and attain strong Bayesian guarantees (in expectation over the prior) when the prior is correct. Such algorithms can also be initialized with some simple `fake' priors; in fact, this is how Thompson Sampling can be made to satisfy the optimal regret bounds.
